---
title: "Overview of Package"
author: "Osama Arshad"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package provides users basic functions to read, summarize and visualize [FARS](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)) data. An overview of basic usage is provided below. Refer to the docs for more details.

## Summarize Observations

We can use this package to summarize FARS data. To obtain a count of the number of accidents for each month in certain years we specify the years of interest to the function `fars_summarize_years`. 

```{r }
BuildingRPackagesAssignment::fars_summarize_years(c(2013, 2014))
```

## Visualize

Can also obtain a plot of the coordiantes of the accidents in a state for a given year using the function `fars_map_state`.

```{r }
BuildingRPackagesAssignment::fars_map_state(1, 2013)
```


